\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
prune text

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classify the presence
or the absence of edges of the graph. Given the ground true adjacency matrix
$A$ and a connectivity score matrix $\hat{A}$, we assess the accuracy of the
network inference method using the area under the ROC curve (AUROC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior
assessment.

>>>>

% Metrics : ROC AUC and AUPRC
In supervised learning terms, the network inference task can be viewed as a
binary classification task where one has to correctly classify the presence
or the absence of edges of the graph. We assess the accuracy of the
network inference method using the area under the ROC curve (AUROC)
and the area under the precision-recall curve (AUPRC)
(\cite{schrynemackers2013protocols}). Since neurons are not self-connected
($(i, i) \not \in E, \forall i \in V$) and some inference methods could
give maximal scores to the diagonal of $\hat{A}$, e.g. Pearson
correlation, we set those elements to the minimum of $\hat{A}$ prior
assessment.
